Effect_size_families

### 2020-06-28 Thesis_Chapter_1/Supp_Material.Rmd
chapter 1 supp. material with markdown

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S2"}
library(ggplot2)
setwd("~/R_projects/Hp_pollen_experiment")
total_pollen <- read.csv("Data/Csv/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="Fig S3"}
par(mar=c(30,13,2,4),xpd=F)
setwd("~/R_projects/Hp_pollen_experiment")
data_percentage <-readRDS("Data/RData/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
abline(v=50,col="black")

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S4"}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
setwd("~/R_projects/Hp_pollen_experiment")
ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Data/RData/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S1"}
library(ggplot2)
setwd("~/R_projects/Hp_pollen_experiment")
total_pollen <- read.csv("Data/Csv/total_pollen.csv")
ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
  geom_bar(stat='identity', position='dodge')+theme_minimal()+
  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="**Fig S3** Average proportion of heterospecific pollen per family for the different 20 treatments counted. On the label of the y-axis, the first family is the pollen recipient family, and the second, the pollen donor family. These pollen ratios are the number of heterospecific pollen grains divided by the total pollen grains per stigma (conspecific and heterospecific pollen) and then averaged by family (N=20). The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
par(mar=c(30,13,2,4),xpd=F)
setwd("~/R_projects/Hp_pollen_experiment")
data_percentage <-readRDS("Data/RData/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
abline(v=50,col="black")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap=""}

par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
setwd("~/R_projects/Hp_pollen_experiment")
ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Data/RData/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

### 2020-06-28 Thesis_Chapter_1/Supp_Material.tex
chapter 1 supp. material with markdown

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\hypertarget{supporting-information}{%
\section{Supporting information:}\label{supporting-information}}

\hypertarget{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}{%
\section{Recipient and donor characteristics govern hierarchical
structure in a heterospecific pollen competition network of co-flowering
plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}}

@@

\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
Species & Common\_names & Variety & Source\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}
\endgroup{}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Fig S2}
\end{figure}

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Fig S3}
\end{figure}

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Fig S4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\textbf{Fig S5} Unipartite bidirectional network with
asymmetrical effect. The lines with the arrow heads connect the impact
of foreign pollen (effect size) of each pollen donor species on each
recipient species. All the arrow heads point to the recipient species of
the reciprocal interaction. Lines of species that did not have a
negative impact are not represented. The different nodes and the donor
species appear coloured by family: Solanaceae (orange), Brassicaceae
(blue) and Convolvulaceae (green). The intensity of the effect is
represented by the line´s size where a larger effect size corresponds to
a thicker line and a thinner line to a smaller effect size. Species
code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa,
SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea,
CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum
lycopersicum, SOME: Solanum melongena.}
\end{figure}

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\section{Supporting information:}\label{supporting-information}

\section{Recipient and donor characteristics govern hierarchical
structure in a heterospecific pollen competition network of co-flowering
plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}

@@

\section{TABLE S1}\label{table-s1}

\begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
Species & Common\_names & Variety & Source\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}

\endgroup{}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Fig S1}
\end{figure}

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\textbf{Fig S3} Average proportion of heterospecific pollen per
family for the different 20 treatments counted. On the label of the
y-axis, the first family is the pollen recipient family, and the second,
the pollen donor family. These pollen ratios are the number of
heterospecific pollen grains divided by the total pollen grains per
stigma (conspecific and heterospecific pollen) and then averaged by
family (N=20). The vertical bar on intercept 50, represents equal
proportions of both recipient (grey) and donor (light blue) pollen.}
\end{figure}

\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\textbf{Fig. S5} Unipartite bidirectional network with
asymmetrical effect. The lines with the arrow heads connect the impact
of foreign pollen (effect size) of each pollen donor species on each
recipient species. All the arrow heads point to the recipient species of
the reciprocal interaction. Lines of species that did not have a
negative impact are not represented. The different nodes and the donor
species appear coloured by family: Solanaceae (orange), Brassicaceae
(blue) and Convolvulaceae (green). The intensity of the effect is
represented by the line´s size where a larger effect size corresponds to
a thicker line and a thinner line to a smaller effect size. Species
code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa,
SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea,
CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum
lycopersicum, SOME: Solanum melongena.}
\end{figure}
